%-------------------------
% Resume in Latex
% Template Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Jacob Portukalian}} & Email : \href{mailto:jportukalian@gmail.com}{jportukalian@gmail.com}\\
  Mobile : +1-626-679-5421 \\
\end{tabular*}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California}{Los Angeles, CA}
      {Bachelor of Science, Electrical Engineering}{June 2011}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Computer Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C, C++, Python, \LaTeX}
    }
    \item{
    	\textbf{Design \& Simulation Tools}{: HFSS, ADS, AWR, Altium, Visio, Powerpoint}
	}
  \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    %==========================================================================================================
    \resumeSubheading
      {Sky Wave Design, LLC}{Los Angeles, CA}
      {Chief Engineer}{April 2014-Nov. 2015, June 2016-Present}
      \resumeItemListStart
      	\resumeItem{Consulting} 
		  {Sky Wave Design is an embedded electronics development consulting business, 
		  focused primarily on embedded systems and Bluetooth Low Energy}
        \resumeItem{Firmware}
          {Expert level embedded firmware developer, especially with Bluetooth LE.  Many firmware projects 
          completed, including systems with complex state-machine behavior that is completely reconfigurable using
          configuration files.  All firmware developed in C for bare metal processors.}
        \resumeItem{Circuit Design}
          {Designed many circuits, from complex sensor data acquisition platforms using a Raspberry Pi, to tiny
          BLE beacons designed to be embedded into a workplace environment for motion detection and reporting.
          All circuits designed in Altium.}
        \resumeItem{PCB Layout}
          {Many layouts performed, both for circuits that we designed in-house, and also some layouts performed
          on their own.  Most complex example was a three PCB stack, each PCB with up to 16 layers, including a 
          switching power supply, FPGA board, and RF transmitter board.}
        \resumeItem{Manufacturing}
          {Most circuits we design get taken all the way through to low volume manufacturing in quantities of up
          to 1000.  We design the production tooling to minimize production costs and time.  We have relationships
          with local vendors to get PCBAs assembled right here in Southern California at affordable prices.  We have
          also taken plastic parts and enclosures through the manufacturing process and had injection molds created.}
        \resumeItem{Certification}
          {Preparing for certification starts with the schematic design.  We have taken products all the way 
          through the complex and painful process successfully.  We know how to ensure your project gets done
          without surprises and setbacks.}
        \resumeItem{Mechanical Design}
          {We are able to design simple mechanical systems and electronics enclosures in 3D and then print
          prototypes using our 3D printer.}
      \resumeItemListEnd
    %==========================================================================================================
    \resumeSubheading
      {FORM Lifting}{Los Angeles, CA}
      {Co-founder / CTO}{June 2015-Nov. 2017}
      \resumeItemListStart
      	\resumeItem{Circuit Design} 
			{Designed a sensor board for a weightlifting collar that included a 6-axis accelerometer and a
			barometric altimeter.  Wrote firmware to stream data back to phone using Bluetooth Low Energy.}
		\resumeItem{Manufacturing} 
			{Produced 1,500 units.  Built and programmed a fixture for automated testing and flashing.
			Had unit FCC/CE/IC/NZ/AUS certified.}
      \resumeItemListEnd
    %==========================================================================================================
    \resumeSubheading
      {Tyvak Nano-Satellites, Inc.}{Irvine, CA}
      {Lead RF Engineer}{Nov. 2015-June 2017}
      \resumeItemListStart
      	\resumeItem{Lead RF Engineer} 
			{As the lead RF engineer I was responsible for all RF development and performance.  Duties included
			new radio designs, supporting off-the-shelf radio sourcing and integration, debugging, link budget
			maintenance, and system design.}
		\resumeItem{System Design}
		    {Designed several systems, including bi-directional low power S-Band links, Space-to-Ground X-Band 
		    telemetry at both low and high data rates, a complete SAR RF chain, including 800W power amplifier.}
		\resumeItem{Transmitter Design}
		    {Designed a complete X-Band transmitter.  Designed hairpin filters and directional couplers in AWR.
		    Simulations matched passive circuit performance on the first try.  Designed low jitter 6 GHz PLL.
		    Laid out all PCBs.  Developed the calibration and integration procedures and assembled and calibrated 
		    flight units for four flight vehicles.  Developed PyQt GUI for controlling the radio to help automate
		    bringup, test, and calibration.}
		\resumeItem{Antenna Design}
		    {Designed deployable 1m S-Band dish that stowed to a 10cm cube.  Designed several patch antennas.
		    Designed helix antenna for UHF and also wrote Python code to take the pattern data and project it
		    to the Earth's surface with an arbitrary rotation for ground coverage analysis.  
		    All designs simulated in HFSS.}
      \resumeItemListEnd
    %==========================================================================================================
    \resumeSubheading
      {Space Exploration Technologies}{Hawthorne, CA}
      {Lead RF Engineer}{Sep. 2011-March 2014}
      \resumeItemListStart
      	\resumeItem{Crew Dragon} 
			{Responsible engineer for designing and implementing the Crew Dragon communication system.  This
			was a clean-slate novel communication system design that met many demanding criteria.  Coordinated
			development effort across many disciplines such as thermodynamics, structures, dynamics, and avionics 
			integration.  Kept design focused on fundamental objective which was
			to close communication links to ground, International Space Station, and TDRSS while also minimizing 
			impact to mass budget.}
		\resumeItem{RF Circuit Design}
			{Designed many RF circuits from scratch.  Designed SDR transmitters and receivers, including
			upconveter and downconverter chains and selecting appropriate DACs/ADCs.  Wrote Python scripts to
			optimize frequency planning.  Designed several filters, both microstrip and lumped-element.  Designed
			a high power PIN diode T/R switch.}
		\resumeItem{PCB Layout}
			{Over 10 PCB layouts for prototype and flight boards for transmitters and receivers.  Most layouts were
			8-12 layers with FPGAs and RF circuits.  Every design was part of a multi-PCB stack and at a minimum
			required compliance with MIL-STD-1540E as well as tough vibration, shock, and thermal environments.}
		\resumeItem{Power Amplifiers}
			{Designed several power amplifiers for UHF and S-Band using both LDMOS and GaN.  Simulated in
			ADS.  Accurately predicted ACPR, mask compliance, and power consumption in ADS which matched 
			measured results.  Achieved over 70\% saturated drain efficiency for S-Band GaN PA.  Designed a multi-PA
			phased array driver with feedback control on both phase and amplitude.}
		\resumeItem{Manufacturing}
			{Designed a test rack for automated transmitter testing.  It was designed to accurately measure
			output power from up to 6 transmitters simultaneously.  Included was a custom designed test set
			and scalar network analyzer for characterizing loads and cables under power.  Wrote Python GUI for 
			running test scripts.}
      \resumeItemListEnd
    %==========================================================================================================
    \resumeSubheading
      {Topanga Technologies}{Canoga Park, CA}
      {Lead RF Engineer}{Feb. 2010-Sep. 2011}
      \resumeItemListStart
	    \resumeItem{Part Time}
			{Majority of employment at Topanga was part-time (30 hours/week) while attending UCLA with a 
			full-time academic load.}
		\resumeItem{Firmware Development}
			{Developed a unique state-machine approach to plasma lighting algorithms.  Designed a system where
			the algorithm was specified in a text file loaded by the firmware.  This allowed any variant of 
			either the lamp or the driver to all use the same version of the firmware.}
		\resumeItem{Circuit Design}
			{Designed a mixed-signal RF driver board that contained a microcontroller and RF source which 
			excited and controlled a 170W UHF power amplifier.  Designed a 5W driver amplifier using LDMOS.}
		\resumeItem{Desktop Software}
			{Developed a suite of applications in C++/Qt for monitoring and controlling drivers, data acquisition,
			database storage, automated inventory management, calibration, and characterization.  Also developed
			software that automated PA characterization, so I was able to generate various sweeps of PA performance
			automatically.}
      \resumeItemListEnd
    %==========================================================================================================
    \resumeSubheading
      {Floor 84 Studio}{North Hollywood, CA}
      {Lead Game Engine Programmer}{Feb. 2008-Dec. 2009}
      \resumeItemListStart
      	\resumeItem{Game Engine} 
			{Designed a 2D game engine for Nintendo DS in C++.  Developed library of 2D widgets such as buttons,
			and other types of graphics.  Wrote all of my own design patterns from scratch.}
		\resumeItem{iOS Apps}
			{Developed several iOS games and apps, including one of the first every DJ mixing and scratching
			sound apps with a sound mixing engine written in C++ (Objective-C was too slow).}
      \resumeItemListEnd
    %==========================================================================================================
  \resumeSubHeadingListEnd
%--------PROGRAMMING SKILLS------------
\section{Patents}
  \resumeSubHeadingListStart
    \item{
      {MULTIPLE PULSE WIDTH MODULATION WAVEFORMS FOR PLASMA LAMP \\
      United States 8957593 \hfill Issued February 7, 2015}
    }
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Extracurriculars}
  \resumeSubHeadingListStart
    \resumeSubItem{Aviation}
      {Private pilot with over 130 hours of flight time.}
    \resumeSubItem{Backpacking}
      {Hiked the John Muir Trail, summer of 2017.  220 miles from Yosemite to Mt. Whitney.}
  \resumeSubHeadingListEnd

%



%-------------------------------------------
\end{document}
